US General Society Survey Analysis

### 2024-03-16 paper/paper.qmd
agains saved scripts and refrences

@@

saveRDS(
  political_preferences,
  file = "political_preferences.rds"
)

political_preferences <-
  readRDS(file = "political_preferences.rds")

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false

@@

saveRDS(
  political_preferences,
  file = "../models/political_preferences.rds"
)

political_preferences <-
  readRDS(file = "../models/political_preferences.rds")
